An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-07 jmiv.tex

\begin{document}
%
\title{A\HT{n Elastica-driven} Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
  \titlerunning{Digital Curve Evolution by Elastica Energy}
  %\title{Digital Curvature Evolution Models for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}

\author{Daniel Antunes\inst{1}
Jacques-Olivier Lachaud\inst{1}
Hugues Talbot\inst{2}}
%
\authorrunning{D. Antunes et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
\email{daniel.martins-antunes, jacques-olivier.lachaud@univ-savoie.fr} \and
CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
\email{hugues.talbot@centralesupelec.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  \HT{Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
    Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
    with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
    binary perimeter prior. It has been observed that this prior is not suitable in many applications, for example for
    segmenting thin objects or some textures, which may have high perimeter/surface ratio. Mumford observed that an
    interesting prior for natural objects is the Euler Elastical model, which involves the squared curvature. In other
    areas of science, researchers have noticed that some physical binarization processes, like emulsion unmixing can be
    well-approximated by curvature-related flow like the Willmore flow. 
    However, curvature-related flows are not easy to compute because curvature is difficult to estimate accurately, and the
    underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
    approximates a curvature-related flow using a multigrid-convergent curvature estimator, within a discrete
    variational framework. We also present an application of this model as a post-processing step in a segmentation
    framework.}
\keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction} %% \todo{(To be extended)}}

@@

One of the first successful uses of \HT{geometric, squared} curvature in image processing is the inpainting algorithm
described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
\HT{optimized with level-sets}.

In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
considered the elastica energy in their ratio-based image segmentation approach. In~\cite{schoenemann2011elastic},
Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
approximated.  \HT{In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
vertebra~\cite{lim2012introducing} using a level-set formulation. They observe improved results compared
to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
solution must also be provided to achieve good results.}

@@

In this paper we are interested in purely discrete variational segmentation models involving an elastica
energy. Recently, new estimators of curvature along digital contours have been proposed
\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the \HT{desirable} multigrid convergence property. This
motivates us to \HT{propose} models in which they can be used successfully.

\HT{In the remainder, we} investigate the use of the digital integral invariant curvature estimator
\cite{coeurjolly13integral} in a discrete variational segmentation framework. More precisely, we show how to incorporate
it in a digital flow minimizing its squared curvature. This model is expressible as a discrete combinatorial
optimization model, which we solve using a classical variant of QPBO algorithm \cite{rother07qpbo}. \HT{Our solution
  does not} compute a global solution to the whole domain, but our approach leads to a digital flow similar to
continuous \HT{Elastica}, as shown by our experiments. We present an application of the model as a post-processing step
in a segmentation framework, and demonstrate how it can improve standard results. The code is freely available on
github\footnote{https://www.github.com/danoan/BTools}.

@@

The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
but the percentage decreases to zero as we set $m$ equal to
$r$. Therefore, we are more confident to take the solution for values
of $m$ close to $r$. However, the way it varies across $m$ values
differs from shape to shape, as is illustrated in figure
\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
$m=r$, all the pixels were labeled. Perhaps this means that our energy
is submodular in this case, but this remains to be proved.

@@

\begin{figure}[!htp]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-square-concavities-probe.eps}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-flower-concavities-probe.eps}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for different radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

\begin{figure}
\center
\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has rougly half the number of pairwise terms  than the lowest ring.\label{fig:ratio-pairwise-terms}}
\end{figure}

\todo{You must comment figure~\ref{fig:ratio-pairwise-terms} in the text.}

@@

 \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; data $(\gamma)$, length $(\alpha)$ and squared curvature $(\beta)$ weights; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
 \BlankLine

 $S \longleftarrow$ GrabCut($I,M$)\;
 $S^{(0)} \longleftarrow $ dilate($S$,$d$)\; 
 \Delta $\longleftarrow +\infty$\;
 $i \longleftarrow 0$\;
 \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{ 	
 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},\gamma,\alpha,\beta$)\;
 	\Delta $\longleftarrow |S^{(i)} - S^{(i+1)}|$\;

@@

 }
 \label{alg:contour-correction} 
 \caption{Contour correction algorithm. \todo{Critère d'arrêt basé sur un nombre de pixels changés !?}}
\end{algorithm}

@@

\begin{figure}
\center
\begin{tabular}{ccc}
Seeds & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/seeds.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq05_dt1_it50.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq1_dt1_it50.png} \\

@@

\begin{figure}
	\center
	\begin{tabular}{ccc}
		GrabCut & Contour Correction & Schoenemann \\
		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}\\									
		\includegraphics[scale=0.2]{images/segmentation/bc/snake/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png}\\						
		\includegraphics[scale=0.2]{images/segmentation/bc/man/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/vase/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png}		
	\end{tabular}
	\caption{The proposed method regularizes grabcut contours and returns meaningful results. We can observe the completion feature of curvature in the second row, and we don't suffer from oversegmentation issues as Schoenemann's method. However, our flow may stop in a local optima as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
	\label{fig:segmentation-results}	
\end{figure}

\begin{figure}
	\center
	\begin{tabular}{ccc}
		GrabCut & Contour Correction & Schoenemann \\
		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png}\\									
		\includegraphics[scale=0.2]{images/segmentation/bc/bird/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png}\\						
		\includegraphics[scale=0.2]{images/segmentation/bc/camel/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/rock/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png}\\
		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png}\\
		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/coral/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png}\\

@@

In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization, and figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} show some segmentation results.

\todo{You must comment on the results.}

>>>>

\begin{document}
%
\title{An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
  \titlerunning{Digital Curve Evolution by Elastica Energy}
  %\title{Digital Curvature Evolution Models for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}

\author{Daniel Antunes\inst{1}
Jacques-Olivier Lachaud\inst{1}
Hugues Talbot\inst{2}}
%
\authorrunning{D. Antunes et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
\email{daniel.martins-antunes, jacques-olivier.lachaud@univ-savoie.fr} \and
CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
\email{hugues.talbot@centralesupelec.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
    Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
    with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
    binary perimeter prior. It has been observed that this prior is not suitable in many applications, for example for
    segmenting thin objects or some textures, which may have high perimeter/surface ratio. Mumford observed that an
    interesting prior for natural objects is the Euler Elastical model, which involves the squared curvature. In other
    areas of science, researchers have noticed that some physical binarization processes, like emulsion unmixing can be
    well-approximated by curvature-related flow like the Willmore flow. 
    However, curvature-related flows are not easy to compute because curvature is difficult to estimate accurately, and the
    underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
    approximates a curvature-related flow using a multigrid-convergent curvature estimator, within a discrete
    variational framework. We also present an application of this model as a post-processing step in a segmentation
    framework.
\keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction} %% \todo{(To be extended)}}

@@

One of the first successful uses of \HT{geometric, squared} curvature in image processing is the inpainting algorithm
described in \cite{masnou98inpainting}\HT{, where authors} evaluate
the absolute curvature along the level lines of a
simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
\HT{optimized with level-sets}.

In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer can help recover thin
and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
considered the elastica energy in their ratio-based image segmentation approach. In~\cite{schoenemann2011elastic},
Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization

framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
approximated.  \HT{In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
vertebra~\cite{lim2012introducing} using a level-set formulation. They observe improved results compared
to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
solution must also be provided to achieve good results.}

@@

In this paper we are interested in purely discrete variational segmentation models involving an elastica
energy. Recently, new estimators of curvature along digital contours have been proposed
\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the desirable multigrid convergence property. This
motivates us to propose models in which they can be used successfully.

\HT{In the remainder, we} investigate the use of the digital integral invariant curvature estimator
\cite{coeurjolly13integral} in a discrete variational segmentation framework. More precisely, we show how to incorporate
it in a digital flow minimizing its squared curvature. This model is expressible as a discrete combinatorial
optimization model, which we solve using a classical variant of QPBO algorithm \cite{rother07qpbo}. \HT{Our solution
  does not} compute a global solution to the whole domain, but our approach leads to a digital flow similar to
continuous \HT{Elastica}, as shown by our experiments. We present an application of the model as a post-processing step
in a segmentation framework, and demonstrate how it can improve standard results. 
\daniel{This paper is an extended version of a previous work that appeared in \cite{antunes19}. We've included a deeper discussion on the optimization method we've used and we present a comparison of our segmentation method with two other related works, and illustrate the results with several examples. Moreover, we have included a new local combinatorial optimization approach for elastica minimization. Finnaly,  the code produced in this paper is freely available on github\footnote{https://www.github.com/danoan/BTools}.}

@@

The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
but the percentage decreases to zero as we set $m$ equal to
$r$. Therefore, we are more confident to take the solution for values
of $m$ close to $r$. However, the way it varies across $m$ values
differs from shape to shape, as is illustrated in figure
\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
$m=r$, all the pixels were labeled, \daniel{which may indicate that $E_r$ is an an easy 
instance of the general non-submodular energy $E_m$, but this remains to be proved. The number of pairwise
terms in $E_r$ is roughly half of those in $E_1$ (see figure \ref{fig:ratio-pairwise-terms}).}

@@

\begin{figure}[h!]
\center
\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has rougly half the number of pairwise terms  than the lowest ring.}
\label{fig:ratio-pairwise-terms}
\end{figure}

\begin{figure}[hp!]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-square-concavities-probe.eps}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-flower-concavities-probe.eps}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for different radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

@@

 \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; length $(\alpha)$, squared curvature $(\beta)$ and data fidelity $(\gamma)$ coefficients; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
 \BlankLine

 $S \longleftarrow$ GrabCut($I,M$)\;
 $S^{(0)} \longleftarrow $ dilate($S$,$d$)\; 
 \Delta $\longleftarrow +\infty$\;
 $i \longleftarrow 0$\;
 \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{ 	
 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},r,\alpha,\beta,\gamma,2$)\;
 	\Delta $\longleftarrow |S^{(i)} - S^{(i+1)}|$\;

@@

 }
 \label{alg:contour-correction} 
 \caption{Contour correction algorithm.}
\end{algorithm}

@@

\begin{figure}[ht!]
\center
\begin{tabular}{ccc}
Seeds & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/seeds.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq05_dt1_it50.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq1_dt1_it50.png} \\

@@

\begin{figure}[ht!]
	\center
	\begin{tabular}{ccc}
		GrabCut & Contour Correction & Schoenemann \\
		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}\\									
		\includegraphics[scale=0.2]{images/segmentation/bc/snake/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png}\\						
		\includegraphics[scale=0.2]{images/segmentation/bc/man/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/vase/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png}		
	\end{tabular}
	\caption{The proposed method regularizes GrabCut contours and returns meaningful results. We can observe the completion feature of curvature in the second row, and we don't suffer from oversegmentation issues as Schoenemann's method. However, our flow may stop in a local optima as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
	\label{fig:segmentation-results}	
\end{figure}

\begin{figure}[hp!]
	\center
	\begin{tabular}{ccc}
		GrabCut & Contour Correction & Schoenemann \\
		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png}\\									
		\includegraphics[scale=0.2]{images/segmentation/bc/bird/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png}\\						
		\includegraphics[scale=0.2]{images/segmentation/bc/camel/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/rock/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png}\\
		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png}\\
		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/coral/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png}\\

@@

\daniel{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization. The curvature can fill gaps and is smoother than the one produced by length only, resulting in more pleasant segmentations. In figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized segmentations and demonstrates the completion property of curvature. Moreover, it does not suffer from over segmentation, it is faster than Schoenemann's, and in several opportunities produces better segmentations than GrabCut.}
